Qubit tests from classical codes

### 2023-03-26 quantum_codes_test.tex
updates in-progress

In this section we give apply the general construction from Section~\ref{sec:main} to a specific quantum-sound code with particularly good parameters, the Reed-Muller code. This was shown sound in~\cite{ji2022quantum} as part of a slightly more general class of ``tensor codes'' shown quantum sound. The resulting qubit test is an important ingredient in the work~\cite{ji2020mip}.

>>>>

In this section we apply the general construction from Section~\ref{sec:main} to a specific quantum-sound code with particularly good parameters, the Reed-Muller code. This was shown sound in~\cite{ji2022quantum} as part of a slightly more general class of ``tensor codes'' shown quantum sound. The resulting qubit test is an important ingredient in the work~\cite{ji2020mip}.
